---
title: "Shiny Application and Reproducible Pitch"
author: "Ahmed Elbaz"
date: "July 13, 2018"
output: ioslides_presentation
---

## Overview

- This presentation is part of the Developing Data Products course final project submission.

- It is an R Markdown documentation generated with R studio to explain how basic mathematical operation application that is created in shiny works. 

- The shiny appliation can be found in https://elbaza286.shinyapps.io/shiny_application_and_reproducible_pitch/

- The ui and server codes used in this project can be found in

## The Application

- The purpose of the application is mainly to take two numbers from the user and show the ouptut of four arithmatic operation on them(Addition, subtraction, multiplication and division).
- The output for a certain operation will be "NA" in case of invalid inputs so please assure that the inputs are numbers and not letters. 

## ui code
In this slide part of ui code was provided noting that the link for complete ui codes were provided in the first slide
```{r, echo = TRUE, eval=FALSE}
library(shiny)
shinyUI(fluidPage(
  # Application title
  titlePanel("Basic Mathematical Operations on two numbers"),
  # Sidebar with a two numeric inputs for 2 numbers
  sidebarLayout(
    sidebarPanel(
       textInput("number1",
                   "Enter the first number:",
                   value = 1),
       textInput("number2",
                    "Enter the second number:",
                    value = 1)

```

## Server code
In this slide part of server code was provided noting that the link for complete server code were provided in the first slide
```{r echo = TRUE, eval=FALSE}
library(shiny)

shinyServer(function(input, output) {

     summation <- reactive({
        x <- as.numeric(input$number1)
        y <- as.numeric(input$number2)
        x + y
    })
    output$output1 <- renderText({
        summation()
    })
})
```

